Regime transition identification for water utilization in river basin developments

### 2020-10-09 tex/main/manuscript.tex
fixed main issues in main manuscript

% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods}) (Figure~\ref{fig:IWRU}).
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (83.7\%), while priority and configuration of the water utilization had slight negative contribution (5.6\% and 10.7\%).
% 第二阶段
In the second period (P2, 1979-1994), though increased positive contributions of priority and configuration (27.8\% and 22.0\% respectively), the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (50.2\% contribution but in negative). 
% 第三阶段
However, as the further increasing of positive contributions of priority (36.1\%) and configuration (38.3\%), and decreases of water stresses in negative contribution (25.6\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress (83.7\%); P2 is priority (27.8\%); and P3 is configuration (38.3\%).

% 三个维度（压力、优先性、配置）的在每年也有各自的变化趋势，将三者结合后，呈现出阶段特征明显
While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig. SX), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C). When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses. After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

Some main drivers caused the above changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S6). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
(2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant. Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B). It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices. As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S6).

% 不断变化的管理模式。
(3) Changing water management practice contributed throughout all three periods. In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S5). Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S5).

@@

\subsection*{Shifted water utilization regimes with development}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S8). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig. S9). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig. S8).
% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted as a transition process towards comprehensive water utilization.

\subsection*{Transition framework towards comprehensive water utilization}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		Transition framework towards a comprehensive water utilization, where water undertakes more socio-economic functions and needs to be considered holistically. Blue paths dominated by a natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic path, water resource are non-provisioning. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 上述过渡过程与稳态转换的关联可能是普遍的
The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic loops are gradually dominating human-water systems in most river basins.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes here, which conceptualizes a general trajectory towards a comprehensive water utilization (Figure~\ref{fig:summary}).
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。

Throughout the transition, three dimensions of water utilization are various in discipline of changes. 
% 水资源压力
(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles in different aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive. In addition to the Yellow River Basin, which is the focus of this study, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, our proposed transitional framework for the nature-society dualistic water cycle is universal in interpreting regime shifts of water utilization.

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% % 资源陷阱和失配，导致崩溃
% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% % 转型应对陷阱
% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% % 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig. S11).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. The resource dilemma revealed after the regime shift, with severe runoff outages(\textit{SI Appendix} Fig. S8).
% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
% 通过协同治理来摆脱困局也普遍存在
Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.

>>>>

% 这一节主要展示IWRU的变化趋势和WUR的划分
With two significant points, the trend of IWRU index are detected into three periods, whose slopes of changing are various and mainly contributed by different dimensions (stress, priority or configuration of water utilization, see \textit{Methods} and \textit{SI Appendix} Methods S4) (Figure~\ref{fig:IWRU}).
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing and the lightening of water stresses made the most striking positive contribution (83.7\%), while priority and configuration of the water utilization had slight negative contribution (5.6\% and 10.7\%).
% 第二阶段
In the second period (P2, 1979-1994), though increased positive contributions of priority and configuration (27.8\% and 22.0\% respectively), the IWRU index experienced a drop because of stresses on water resource playing a larger negative role (50.2\% contribution but in negative). 
% 第三阶段
However, as the further increasing of positive contributions of priority (36.1\%) and configuration (38.3\%), and decreases of water stresses in negative contribution (25.6\%) in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period has a different most striking positive contributor to IWRU: P1 is stress (83.7\%); P2 is priority (27.8\%); and P3 is configuration (38.3\%).

% 三个维度（压力、优先性、配置）的在每年也有各自的变化趋势，将三者结合后，呈现出阶段特征明显
While the above three dimensions (stress, priority and configuration) also have own variation (see \textit{SI Appendix} Methods S4 and Fig. S4), combination of their contribution ratios clustered clearly by different time periods, indicating three regimes (Figure~\ref{fig:phases}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{../../figures/main/phases.pdf}
	\caption{Combination of contributions regards three dimensions in different periods (S: stresses; P: priority; C: configuration). The closer a point to an angle of the triangle, greater the proportion of the contribution of this dimension.
	The red indicator line in this ternary plot denotes 1:1 contributions between priority (P) and configuration (C). When the points are bellow this line, the contribution ratio of configuration is lower than that of priority, and vice versa.}
	% 由于阶段一的点位于该线上方，L的净贡献比例多于P，而第二阶段的点则恰好相反。
	\label{fig:phases}
\end{figure}
% 第一阶段到第二阶段
At the very beginning (1965) and throughout the whole P1, water utilization regime dominated by high stresses. After then, it experienced a shift to low stresses since 1978, with a change in the proportion of contributions between priority and configuration, too.
% 第三阶段集中
Finally, the contribution of three dimensions were much similar in P3 (32.91\%, 31.87\% and 35.21\% for priority, configuration and stress respectively), making the points highly concentrated at the centre of the ternary diagram in that period.

@@

Some main drivers caused the above changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the priority of water utilization between P1 and P2 (Figure\ref{fig:Causes}A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6 ha/yr$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978, see \textit{SI Appendix} Fig. S7). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water (\textit{SI Appendix} S7).

% 用水关系的变化
(2) During the P3, irrigation had noticeable changes in its efficiency, whose water consumptions were reduced but still dominant. Although irrigated area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes}A and Figure~\ref{fig:Causes}B). It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (\textit{SI Appendix} Fig. S8). As a result, the differences between the sectors of water use reduced while the total water consumption remains stable, during the P3 (\textit{SI Appendix} Fig. S7).

% 不断变化的管理模式。
(3) Changing water management practice contributed throughout all three periods. In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).

@@

\subsection*{Shifted water utilization regimes with development}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S9). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was dried up for the first time with a length of 310 km for 19 days, and continued to be dried up for many years since then (\textit{SI Appendix} Fig. S10). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig. S9).
% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement are intertwined in human-water system. Since they have driven the YRB to change regimes twice between 1965 and 2013 along with social development, it can be interpreted as a transition process towards comprehensive water utilization.

\subsection*{Transition framework in water utilization}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		Transition framework towards a comprehensive water utilization, where water undertakes more socio-economic functions and needs to be considered holistically. Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. 
		\textbf{A. Natural phase:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic path, water resource are non-provisioning. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

% 上述过渡过程与稳态转换的关联可能是普遍的
The association between the above transition process and the regime shifts of water utilization may be pervasive as socio-economic pathways are gradually dominating human-water systems in most river basins.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework, which conceptualizes a general trajectory towards a comprehensive water utilization where regional socio-economic pathways dominating stage by stage (Figure~\ref{fig:summary}).
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。

Throughout the transition phases, three dimensions of water utilization are various in discipline of changes. 
% 水资源压力
(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive. In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% % 资源陷阱和失配，导致崩溃
% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% % 转型应对陷阱
% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% % 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig. S11).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
% 后来摆脱了资源陷阱（表现形式 xxx）。
As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
% 通过协同治理来摆脱困局也普遍存在

% 此外，即使发展极大提升了用水效率，黄河流域的困境也并没能完全解决。
In addition, further dilemmas has not been completely solved as basins developments tighter interlinked to the ecosystems after integrated management and move to a regional phase (refers from a local phase to a regional phase in the framework, Figure~\ref{fig:summary}).
% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，倾向性停滞，灵活性进一步降低，）
% Therefore, basins still in need of further transformations according to changes within the transition cycle of water utilization. 
Firstly, in line with paradox of irrigation efficiency, significant improvement in agricultural irrigation efficiency has been accompanied by re-growths in irrigated area, resulting in a usually unabated trend of water resources stress \cite{graftonParadoxIrrigationEfficiency2018}. 
Secondly, the changing priority between non-provisioning (i.e. industry or services) and provisioning (i.e. domestic and irrigation water use) may rigidify the inflexibility of water use \cite{qinFlexibilityIntensityGlobal2019}.
Take the YRB as an example again, after getting rid of the resource dilemma, the stresses on water resources were still growing, while inflexible water use (domestic and thermal uses) growth most strikingly (supplementary Fig. S4). 
% 这可能对全球的流域都是一个警示，因为
It can be a warning to river basins around the world in comprehensive developments, since these may lead to a reduction in resilience of basins and leave highly coupled human-water systems facing greater vulnerability to collapse --as a structural dilemma \cite{cummingResilienceBigRiver2011}.

% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Taken together, based on the identification of current phases and development dilemmas by the transition framework, further transformative governance is still needed to achieve a high-quality sustainable development of the basin, because development is not a panacea for every dilemma \cite{scoonesTransformationsSustainabilityCombining2020a}.
